A Survey of Quantitative Descriptions of Molecular Structure

### 2012-07-24 paper.tex
Added a nice intro figure to the paper
made sure to refer to the figure in the text;

Methods that aim to predict chemical and biological properties
generally require a numerical description of chemical structures. Such
numerical forms range from a set of 3D coordinates which coupled with
appropriate atom types, is sufficient for methods such as quantum
mechanical (QM) approaches and docking to more abstract numerical
descriptions derived from 2D or 3D representations which can be useful
in statistical approaches. It is now possible to evaluate thousands of
numerical descriptors of chemical structure. As will be discussed
later, many of these descriptors are closely related or capture the
same information, allowing one to be substituted for another. The
selection of relevant descriptors is a well-known problem and given a
large collection of them, approaches to identify a suitable subset
have been discussed extensively in the
literature~\cite{Miller:2002aa,Kohavi:1997gf}.

@@

>>>>

Methods that aim to predict chemical and biological properties
generally require a numerical description of chemical structures. Such
numerical forms range from a set of 3D coordinates which coupled with
appropriate atom types, is sufficient for methods such as quantum
mechanical (QM) approaches and docking to more abstract numerical
descriptions derived from 2D or 3D representations which can be useful
in statistical approaches.  It is now possible to evaluate thousands
of numerical descriptors of chemical structure. As will be discussed
later, many of these descriptors are closely related or capture the
same information, allowing one to be substituted for another. The
selection of relevant descriptors is a well-known problem and given a
large collection of them, approaches to identify a suitable subset
have been discussed extensively in the
literature~\cite{Miller:2002aa,Kohavi:1997gf}.  Figure \ref{fig:repr}
is a summary depiction of the major types of descriptors and the form
of molecular structure information that is required to compute
them. The depiction is very general and focuses on small molecule
descriptors. As will be described in the following sections, molecular
descriptors can be calculated for many chemical entities, not just
small organic molecules.

@@

\ctable[caption={A graphical summary of descriptor types and the type
  of input information required. As one goes from top to bottom the
calculations become more intensive, but the results capture aspects of
molecular structure more realistically.}, cap={}, botcap,figure, label={fig:repr}]
{c}
{}
{
\includegraphics[width=0.9\linewidth]{oss-desc-repr}
}
